Comparing Generative Pre-trained Transformer Models to Physicians for Assigning Causes of Death from Verbal Autopsy: A Case Study of 6939 Deaths in Sierra Leone from 2019-2022

### 2024-04-04 manuscript/manuscript.tex
Add sampling map from cheryl
Edit map fig text
Starting edits from feedback after gpt rereuns from andy

@@

\begin{table}[h]
\caption{Overall model performance for physician agreed records (n=6939)}\label{tab-perf-overall}%
\begin{tabular}{@{}llll@{}}
\toprule
Model & PCCC  & CSMF Accuracy & PCCC Improvement from Model Below\\
\midrule
GPT-4 & 0.71 & 0.89 & $\uparrow$ 0.07\\
GPT-3.5 & 0.64 & 0.86 & $\uparrow$ 0.20\\
InSilicoVA & 0.44 & 0.74 & $\uparrow$ 0.01\\
InterVA-5 & 0.43 & 0.78 & -\\
\botrule
\end{tabular}
\footnotetext{Note: Models sorted from highest to lowest PCCC.}
\end{table}

>>>>

\begin{figure}[h!]
\centering
\includegraphics[width=1\textwidth]{fig-data-sampling.pdf}
\caption{Case study sample areas. VA records were collected from sample areas in Sierra Leone between 2019-2022 from the HEAL-SL study. Sample deaths shown represent records with physician assigned CODs only.}\label{fig-data-sampling}
\end{figure}

@@

\begin{table}[h]
\caption{Overall model performance for physician agreed records (n=6939)}\label{tab-perf-overall}%
\begin{tabular}{@{}llll@{}}
\toprule
Model & PCCC  & CSMF Accuracy & PCCC Improvement\\
\midrule
GPT-4 & 0.61 & 0.79 & $\uparrow$ 0.03\\
GPT-3.5 & 0.58 & 0.74 & $\uparrow$ 0.14\\
InSilicoVA & 0.44 & 0.74 & $\uparrow$ 0.01\\
InterVA-5 & 0.43 & 0.78 & -\\
\botrule
\end{tabular}
\footnotetext{Note: Models sorted from highest to lowest PCCC. Improvements are from model below.}
\end{table}
